Approximation as Differentiation notes

### 2025-04-02 notes/sec/biproduct.tex
Tweaks to biproducts.

Suppose $C$ a $\CMon$-enriched category. \todo{I think we can also define ``biproduct'' just using zero
morphisms, and then derive rather than assume $\CMon$-enrichment.}

\begin{definition}[Biproduct]
For any objects $A, B$, the \emph{biproduct} of $A$ and $B$ is an object $A \biprod B$ of $C$ together with
morphisms

@@

\noindent We say that $C$ is \emph{semi-additive} if it has finite biproducts. Having products or coproducts
is sufficient for semi-additivity.

>>>>

\begin{definition}[Biproduct]
Suppose $C$ a $\CMon$-enriched category. For any objects $A, B$, the \emph{biproduct} of $A$ and $B$ is an
object $A \biprod B$ of $C$ together with morphisms

@@

\noindent \todo{I think we can also define ``biproduct'' just using zero morphisms, and then derive rather
than assume $\CMon$-enrichment.}

We say a $\CMon$-enriched $C$ is \emph{semi-additive} if it also has finite biproducts; having products or
coproducts is sufficient.
